$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-03-29 paper/e6ssm-tuning-paper.tex
on less --> less on.

This demonstrates two important points about these $U(1)$
extensions. Firstly that limits on the $Z^\prime$ mass play an
incredibly important role in constraining natural scenarios in such
models and secondly that the tuning from the $Z^\prime$ limits in
these models depends on less assumptions about SUSY breaking than the
tuning required by the $125$ GeV Higgs measurement which concerns
people in the MSSM.

@@

We also looked at the tuning in different $U(1)$ extensions for fixed
$\tan \beta = 10$.  We found that in every case except for the
$U(1)_I$ the fine tuning was much worse for the larger $Z^\prime$
mass, further emphasising the importance of this in $U(1)$ extensions.
The $U(1)_I$ model showed the least tuning due to
the vanishing charge of the $H_u$ state. This model is quite
interesting in the sense that it provides a solution to the
$\mu$-problem while avoiding the large tuning (with current limits)
from the $Z^\prime$ mass. However one should remember we are looking
at conservative limits on naturalness here and there is no solution to
the usual tuning coming from the large stops needed to get a $125$ GeV
Higgs in this model.

>>>>

This demonstrates two important points about these $U(1)$
extensions. Firstly that limits on the $Z^\prime$ mass play an
incredibly important role in constraining natural scenarios in such
models and secondly that the tuning from the $Z^\prime$ limits in
these models depends less on assumptions about SUSY breaking than the
tuning required by the $125$ GeV Higgs measurement which concerns
people in the MSSM.

@@

We also looked at the tuning in different $U(1)$ extensions for fixed
$\tan \beta = 10$.  We found that in every case except for the
$U(1)_I$ the fine tuning was much worse for the larger $Z^\prime$
mass, further emphasising the importance of this in $U(1)$ extensions.
The $U(1)_I$ model showed the least tuning due to
the vanishing charge of the $H_u$ state. This model is quite
interesting in the sense that it provides a solution to the
$\mu$-problem while avoiding the large tuning (with current limits)
from the $Z^\prime$ mass. However one should remember we are looking
at conservative limits on naturalness here and there is no solution to
the usual tuning coming from the large stops needed to get a $125$ GeV
Higgs in this model, which will be a problem as the UV scale is raised.
